An Exposition on the Propriety of Restricted Boltzmann Machines

### 2016-07-28 presentations/jsm2016/index.Rmd
scaled densities for slides

all_statistics %>%
  gather(statistic, value, -iter, -method, -starts_with("v")) %>%
  filter(grepl("image", statistic) & !is.na(value)) %>%
  separate(statistic, into = c("junk", "statistic")) %>%
  mutate(statistic = factor(statistic, labels = paste("Image", 1:length(unique(statistic))))) %>%
  left_join(distn_good %>% select(-image_id)) %>% 
  ggplot() +
  geom_density(aes(value, colour = method, fill = method), alpha = .2) +
  geom_vline(aes(xintercept = prob)) +
  facet_wrap(~statistic, scales = "free_x") + 
  ylab("Posterior Density") + xlab("Probability of Image") +
  scale_colour_discrete("Method", labels = c("Marginalized likelihood", "Trick prior", "Truncated Normal prior")) +
  scale_fill_discrete("Method", labels = c("Marginalized likelihood", "Trick prior", "Truncated Normal prior")) -> p.models
```
```{r models-plot, fig.width=8, fig.height=4}
p.models
```
Each of these rigorous fitting methods seeks to merely replicate the empirical data distribution, which is the optimal nonparametric solution.

>>>>

all_statistics %>%
  gather(statistic, value, -iter, -method, -starts_with("v")) %>%
  filter(grepl("image", statistic) & !is.na(value)) %>%
  separate(statistic, into = c("junk", "statistic")) %>%
  mutate(statistic = factor(statistic, labels = paste("Image", 1:length(unique(statistic))))) %>%
  left_join(distn_good %>% select(-image_id)) %>% 
  ggplot() +
  geom_density(aes(value, y=..scaled.., colour = method, fill = method), alpha = .2) +
  geom_vline(aes(xintercept = prob)) +
  facet_wrap(~statistic, scales = "free_x") + 
  ylab("Scaled Posterior Density") + xlab("Probability of Image") +
  scale_colour_discrete("Method", labels = c("Marginalized likelihood", "Trick prior", "Truncated Normal prior")) +
  scale_fill_discrete("Method", labels = c("Marginalized likelihood", "Trick prior", "Truncated Normal prior")) -> p.models
```
```{r models-plot, fig.width=8, fig.height=4}
p.models
```
Each of these rigorous fitting methods seeks to merely replicate the empirical data distribution, which is the optimal nonparametric solution.
